Reading Notes

### 2020-07-29 reading-notes.tex
adding a bunch of papers to compare data to

\cite{Levitt1976}
one cg bead per residue

\cite{McCoy1998a}
\bibliography{library}
\bibliographystyle{ieeetr}
\end{document}

>>>>

\cite{Levitt1976}
protein cg model--backbone represented by 3 beads (alpha-C, O, N) one bead per sidechain. protein sequence dictates folding so simplifying to one bead per amino acid seems reasonable. challenges: too many atoms, proteins fold in water at RT (opposed to small molecule crystals which can be calculated in vacuum at low temp)

\cite{McCoy1998a}
backmapping from UA to AA. ugh maybe skip this.

\cite{Yi2018a}
PTB7-Th:ITIC/SF-PDI4 PCEs, mobilities, 1D scattering

\cite{S.Gurney2019b}
PTB7-Th ITIC PCE scattering patterns

\cite{Swick2019a}
ITIC derivatives, dft, crystal structures

\cite{Hammond2011a}
PTB7:PC71BM scattering PCE

\cite{Qin2016}
P3HT, PDCBT:ITIC scattering PCE

\cite{Pan2018c}
ITIC: PBDB-T and PBQ-0F molecular dynamics and dft

\cite{Shi2017d}
4TIC, PTB7-Th PCE scattering

\cite{Wang2019c}
PBTZF4, ITIC-Th experimental PCE values, mobilities

\bibliography{library}
\bibliographystyle{ieeetr}
\end{document}
